---
title: "unit-test-practice"
format: html
editor: visual
---

### Unit testing with the `testthat` package

First, install necessary packages
```{r}
install.packages("testthat")
install.packages("devtools")
install.packages("remotes")

```
```{r}
library(testthat)
library(devtools)
library(remotes)
```
Write a function to practice unit tests.
This function is going to find the mean value of each column, and then return the lowest and highest mean value calculated (in that order)
We would expect:
- the output to be numeric
- output should be a vector of length 2
- the first value should be smaller than the second value

```{r}
mean_range <- function(df) {
  # return the mean vlaues of each column
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE)
  
  # Find minimum and maximum values
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  
  # Return min and max values in that order
  return(c(col_mean_min, col_mean_max))
}

mean_range(df = mtcars)
```
Write some tests!
```{r}
#| echo: false
# Test that the output is of length 2
expect_length(mean_range(df = mtcars), 2)

# Test that first value is less than second value
expect_true(mean_range(mtcars)[1] < mean_range(mtcars)[2])
```


